---
title: "visualization_ggplot2"
author: "Jaisal Amin"
date: "9/27/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggridges)
```

## Load data

```{r data_import, cache = TRUE}
library(rnoaa)

weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
weather_df
```

## Start a plot

Blank plot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax))
```

Scatterplot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

```{r}
weather_df %>% 
  filter(name == "CentralPark_NY") %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

Naming plots:

```{r}
weather_sp = 
  ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

## More plot options

Add an aesthetic

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))
```

Add a line through the middle of plot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name)) + 
  geom_smooth(se = FALSE)
```

Change point transparency:

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = 0.4) + 
  geom_smooth(se = FALSE)
```

Apply aesthetic mapping for color globally:

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = 0.4) + 
  geom_smooth(se = FALSE)
```

Facetting:

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax, color = name)) + 
  geom_point(alpha = 0.4) + 
  geom_smooth(se = FALSE) + 
  facet_grid( ~ name)
```

A more interesting plot:

```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_line()
```


```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name, size = prcp)) + 
  geom_point(alpha = 0.3) + 
  geom_smooth(se = FALSE) + 
  facet_grid ( ~ name)
```

## Univariate plots

Histograms:

```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_histogram()
```

Density plots:

```{r}
ggplot(weather_df, aes(x = tmax, fill = name)) + 
  geom_density(alpha = 0.5)
```

Boxplots:

```{r}
ggplot(weather_df, aes(x = name, y = tmax)) +
  geom_boxplot()
```

Violin plots:

```{r}
ggplot(weather_df, aes(x = name, y = tmax)) + 
  geom_violin(aes(fill = name), color = "blue", alpha = .5) + 
  stat_summary(fun.y = median, geom = "point", color = "blue", size = 4)
```

Ridge plots:

```{r}
ggplot(weather_df, aes(x = tmax, y = name)) + 
  geom_density_ridges()
```

## Last example

Making multiple plots:

```{r}
ggplot(weather_df, aes(y = prcp, x = name)) +
  geom_boxplot()
```

Not so great...

```{r}
weather_df %>% 
  filter(prcp < 50) %>% 
  ggplot(weather_df, aes(x = prcp, fill = name)) +
  geom_density(alpha = .5)
```


